Experiment 3 of 4

### 2016-08-02 experiments/e0/writeup/e0.Rmd
no reshape only reshape2

```{r loadLibraries}
suppressPackageStartupMessages(library(MASS))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(lme4))
suppressPackageStartupMessages(library(xtable))
suppressPackageStartupMessages(library(plyr))
suppressPackageStartupMessages(library(reshape))
suppressPackageStartupMessages(library(lattice))
suppressPackageStartupMessages(library(LMERConvenienceFunctions))
suppressPackageStartupMessages(library(car))
suppressPackageStartupMessages(library(gridExtra))
suppressPackageStartupMessages(library(grid))
suppressPackageStartupMessages(library(lmerTest))
```

>>>>

```{r loadLibraries}
suppressPackageStartupMessages(library(MASS))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(lme4))
suppressPackageStartupMessages(library(xtable))
suppressPackageStartupMessages(library(plyr))
suppressPackageStartupMessages(library(reshape2))
suppressPackageStartupMessages(library(lattice))
suppressPackageStartupMessages(library(LMERConvenienceFunctions))
suppressPackageStartupMessages(library(car))
suppressPackageStartupMessages(library(gridExtra))
suppressPackageStartupMessages(library(grid))
suppressPackageStartupMessages(library(lmerTest))
```

### 2016-08-02 experiments/e3/writeup/e3.Rmd
no reshape only reshape2

```{r loadLibraries}
suppressPackageStartupMessages(library(MASS))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(lme4))
suppressPackageStartupMessages(library(xtable))
suppressPackageStartupMessages(library(plyr))
suppressPackageStartupMessages(library(reshape))
suppressPackageStartupMessages(library(lattice))
suppressPackageStartupMessages(library(LMERConvenienceFunctions))
suppressPackageStartupMessages(library(car))
suppressPackageStartupMessages(library(grid))
suppressPackageStartupMessages(library(lmerTest))
suppressPackageStartupMessages(library(reshape2))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(require(languageR))
```

@@

```{r boxplot subjects and items}
load("data.Rda")
# allow reference to transformation
subdata = melt(dd,
               measure.vars=c("RT_Rec", "RT_RecSqt", "RT_log", "RT_raw"),
               variable.name="transformation",
               value.name="value") 
# boxplots for subjects and items separately for each dependent variable
ggplot(subdata) + 
  facet_wrap(~ variable, scales="free", ncol=4) +
  geom_boxplot(aes(y=value, x=Item, col="Items")) + 
  geom_boxplot(aes(y=value, x=Subject, col="Subjects")) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), aspect.ratio=1, panel.grid=element_blank()) + 
  scale_colour_manual("",values=c("Items"="red","Subjects"="blue")) +
  xlab("") + ylab("")
```

>>>>

```{r loadLibraries}
suppressPackageStartupMessages(library(MASS))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(lme4))
suppressPackageStartupMessages(library(xtable))
suppressPackageStartupMessages(library(plyr))
suppressPackageStartupMessages(library(lattice))
suppressPackageStartupMessages(library(LMERConvenienceFunctions))
suppressPackageStartupMessages(library(car))
suppressPackageStartupMessages(library(grid))
suppressPackageStartupMessages(library(lmerTest))
suppressPackageStartupMessages(library(reshape2))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(require(languageR))
```

@@

```{r boxplot subjects and items, width-12, height=3}
load("data.Rda")
# allow reference to transformation
subdata = melt(dd,
               measure.vars=c("RT_Rec", "RT_RecSqt", "RT_log", "RT_raw"),
               variable.name="transformation",
               value.name="value") 
# boxplots for subjects and items separately for each dependent variable
ggplot(subdata) + 
  facet_wrap(~ transformation, scales="free", ncol=4) +
  geom_boxplot(aes(y=value, x=Item, col="Items")) + 
  geom_boxplot(aes(y=value, x=Subject, col="Subjects")) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), aspect.ratio=1, panel.grid=element_blank()) + 
  scale_colour_manual("",values=c("Items"="red","Subjects"="blue")) +
  xlab("") + ylab("")
```
